---
title: "p8105_hw1_yc4384"
author: "Yangyang Chen"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem_1


#Introduce the dataset

```{r}
library(moderndive)
data("early_january_weather") #load dataset
summary(early_january_weather) #the variables in this dataset, including names / values of important variables
```

* There are `r ncol(early_january_weather)` variables in the dataset. The variable 'origin' is an character type variable, and variable 'wind_gust' includes all NA values.
* The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.
* The mean of 'temp' is `r round(mean(early_january_weather$temp),2)`.

```{r}
#Scatterplot of dataset and save image
library(ggplot2)
scatter_plot = ggplot(early_january_weather, aes(x = time_hour, y= temp, color = humid)) #color points using the humid variable
scatter_plot + geom_point()
```

* The temperature is non-stationary, and it is periodically fluctuated increasing from Jan_01 to Jan_15.

```{r}
ggsave("scatterplot.png", plot = scatter_plot + geom_point(), width = 6, height = 4) #Export scatterplot to the project directory
```


## Problem_2
```{r}
#Create a dataset
v1 = rnorm(10) #a random sample of size 10 from a standard Normal distribution
v2 = ifelse(v1>0, "T", "F") #a logical vector indicating whether elements of the sample are greater than 0
v3 = c('a','b','c','d','e','f','g','h','i','j') #a character vector of length 10
v4 = as.factor(c(1,2,3,3,2,1,2,3,1,3)) #a factor vector of length 10, with 3 different factor “levels”
df = data.frame(v1,v2,v3,v4) #create a data frame
df

#Compute mean of each vector
library(tidyverse)# Use pull() to extract the each column as a vector
vector <- df %>% pull(v1)
mean(vector)
vector <- df %>% pull(v2)
mean(vector)
vector <- df %>% pull(v3)
mean(vector)
vector <- df %>% pull(v4)
mean(vector)

# Convert variables from one type to another and calculate their means
vector <- df %>% pull(v2)
mean(as.numeric(as.factor(vector)))
vector <- df %>% pull(v3)
mean(as.numeric(as.factor(vector)))
vector <- df %>% pull(v4)
mean(as.numeric(vector))

```
* Since v2 and v3 are converted to numeric values. their means can be computed.

